\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-18 using.tex
more copyedit
more

\revision{Both of these functions are predicates on the guest kernel's execution state (usually on the contents of its scheduler's data structures). Example implementations are given in Figure~\ref{fig:student-c}.}

@@

\begin{itemize}
	\item \texttt{within\_function}: If the user configures decision points to happen in common code paths, such as \texttt{mutex\_lock}, it will likely generate more branching than needed. For example, if testing \texttt{vanish}, there's no need to branch on a \texttt{mutex\_lock} in \texttt{exec}.

>>>>

\revision{Both of these functions are predicates on the guest kernel's execution state, usually on the contents of its scheduler's data structures. Example implementations are given in Figure~\ref{fig:student-c}.}

@@

\begin{itemize}
	\item \texttt{within\_function}: If the user configures decision points to happen in common code paths, such as \texttt{mutex\_lock}, it will likely generate more branching than needed. For example, if testing \texttt{vanish}, the user may judge there to be no need to branch on a \texttt{mutex\_lock} in \texttt{exec}.
